\huge A Usability Evaluation of Tor Launcher

### 2016-10-24 pets2017-paper/pets2017-paper.tex
introductory sentences for sections.

\section{Background}
\label{sec:background}
This section discusses network components involved in connecting to Tor, network conditions that require these network components, and the set of valid ways to connect to Tor.

@@

\section{Formative Usability Testing}
\label{sec:qualitative}

{\color {blue}
short intro sentence
}
\subsection{Recruitment}
We recruited people from Craigslist using the recruitment text in Appendix~\ref{qualitative-recruitment}, which linked an presecreening survey that collected demographics (Appendix~\ref{qualitative-prescreening}). We pre-screened~\cite{screening} for diversity in gender, age, technical expertise, use of security tools, and familiarity with Tor in a small participant pool. Of our 16 recruited participants, 53.3\% were male. Ages ranged from 20 to~62 years ($\mu = 24.5$, $\sigma = 12.6$). 93.3\% of our participants had college education. We took participants' self-reported familiarity with technical terms use of security tools with skepticism (Appendix~\ref{prescreening-responses}). We verified their self-reported familiarity with Tor Browser in-person, and found that 4 used it, 5 heard of it but not used it, and the remaining 8 never heard of or used it.

@@

\section{Design Principles and Changes}
\label{sec:design}

{\color {blue}
Introductory sentence.
}

@@

\section{Summative Usability Testing}
\label{sec:quantitative}

{\color {blue} 
short intro sentence.
}

>>>>

\section{Background}
\label{sec:background}
This section discusses network components involved in connecting to Tor, network conditions that require specific network components, and how to configure the involved network components.

@@

\section{Formative Usability Testing}
\label{sec:qualitative}
This section discusses our small-scale, qualitative usability evaluation and resulting user insights.

\subsection{Recruitment}
We recruited people from Craigslist using the recruitment text in Appendix~\ref{qualitative-recruitment}, which linked an presecreening survey that collected demographics (Appendix~\ref{qualitative-prescreening}). We pre-screened~\cite{screening} for diversity in gender, age, technical expertise, use of security tools, and familiarity with Tor in a small participant pool. Of our 16 recruited participants, 53.3\% were male. Ages ranged from 20 to~62 years ($\mu = 24.5$, $\sigma = 12.6$). 93.3\% of our participants had college education. We took participants' self-reported familiarity with technical terms use of security tools with skepticism (Appendix~\ref{prescreening-responses}). We verified their self-reported familiarity with Tor Browser in-person, and found that 4 used it, 5 heard of it but not used it, and the remaining 8 never heard of or used it.

@@

\section{Design Principles and Changes}
\label{sec:design} 
This section discusses how we converted our formative usability testing observations into design changes.

@@

\section{Summative Usability Testing}
\label{sec:quantitative}
This section discusses our large-scale quantitative usability evaluation and resulting user measurements.
